### 2025-04-13 basic-statistics.qmd
20250413 - distribution visualizer

>>>>

You can use the following web application to visualize various distributions according to a specified [center](#sec-descriptiveStatisticsCenter) (mean), [spread](#sec-descriptiveStatisticsSpread) (standard deviation), and [shape](#sec-descriptiveStatisticsShape) (skewness and kurtosis):

```{=html}
<iframe id="distributionVisualizer" src="https://ffashiny.shinyapps.io/distributionvisualizer/" style="border: none; width: 100%; height: 100%" frameborder="0"></iframe>
```
